The classical mutual information in mean-field spin glass models

### 2015-07-03 sk_model_v18.tex
revised-3/07/2015

We investigate the \emph{classical} R\'enyi entropy $S_n$ and the associated mutual 
information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
paradigm model of mean-field spin glasses. 
Using classical Monte Carlo simulations and analytical tools we investigate the 
S-K model on the $n$-sheets booklet.
This is obtained by gluing together $n$ independent copies of the model, and it is the 
main ingredient to construct the R\'enyi entanglement-related quantities. We find a 
glassy phase at low temperature, whereas at high temperature the model exhibits 
paramagnetic behavior, consistent with the regular S-K model. The temperature of the 
paramagnetic-glassy transition depends 
non-trivially on the geometry of the booklet. At high-temperatures we provide the exact 
solution of the model by exploiting the replica symmetry. This is the permutation symmetry 
among the fictitious replicas that are used to perform disorder averages (via the replica 
trick). In the glassy phase the replica symmetry has to be broken. Using a generalization 
of the Parisi solution, we provide analytical results for $S_n$ and ${\mathcal I}_n$, 
and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
volume law in the whole phase diagram. We fully characterize the behavior of the 
corresponding densities $S_n/N,{\mathcal I}_n/N$, in the thermodynamic limit. 
Interestingly, at the critical point the mutual information does not exhibit any 
crossing for different system sizes, in contrast with local spin models.

@@

Besides being ubiquitous in nature, disorder leads to several intriguing 
physical phenomena. 
Arguably, \emph{spin glasses} represent one of the most prototypical examples
of exotic behavior induced by disorder.
While at any finite temperature disorder can prevent the 
usual magnetic ordering, at low-enough temperatures these systems display a 
new type of ``order''. In the past decades an intense theoretical 
effort has been devoted to characterizing this spin glass order, the nature of 
the paramagnetic-glassy transition, and that of the associated order 
parameter~\cite{binder-1986,parisi-book,young-1998,nishimori-book,castellani-2005}.

All these issues can be thoroughly addressed in the Sherrington-Kirkpatrick 
(S-K) model~\cite{sherrington-1978,sherrington-1978-prl}, which is exactly 
solvable. The S-K model is a \emph{classical} Ising model on the fully-connected 
graph of $N$ sites, with quenched random interactions. Its hamiltonian reads  
%
\begin{equation}
{\mathcal H}=-\sum\limits_{1\le i<j\le N}J_{ij}S_i S_j-
h\sum\limits_{1\le i\le N}S_i.
\label{SK-intro}
\end{equation}
%
Here $S_i=\pm 1$ are classical Ising spins, $h$ is an external magnetic field, and 
$J_{ij}$ are uncorrelated (from site to site) random variables. The S-K model hosts 
a low-temperature glassy phase, which is separated from a high-temperature paramagnetic 
one by a second order phase transition. Despite its mean-field nature, the solution 
of the S-K model has been a mathematical challenge. Although it was proposed as an 
ansatz by Parisi~\cite{parisi-1980} more than thirty years ago, its rigorous proof 
was obtained only recently~\cite{talagrand-2006}. Moreover, the solution exhibits several 
intricate features, such as lack of self-averaging~\cite{pastur-1991}, ultrametricity~\cite{
mezard-1984,rammal-1986}, and replica symmetry breaking~\cite{parisi-book,castellani-2005}. 
The last refers to the breaking of the permutation symmetry among the fictitious replicas 
of the model, which are introduced to perform disorder averages (via the so-called 
\emph{replica trick}~\cite{cardy-book}, not to be confused with the replica trick used 
in calculating the R\'enyi entanglement entropies). Finally, although the 
applicability of the S-K model to describe realistic spin glasses is still highly 
debated~\cite{yucesoy-2012,billoire-2012,yucesoy-2013}, there are recent proposals on 
how to realize it in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser 
systems~\cite{ghofraniha-2015}.

In the last decade entanglement-related quantities emerged as valuable tools to 
understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
cc-rev}, both classical and quantum. For instance, at a conformally invariant critical 
point entanglement measures contain universal information about the underlying 
conformal field theory (CFT), such as the central charge~\cite{holzhey-1994,vidal-2003,
calabrese-2004,calabrese-2012}. For classical spin models a lot of attention has been 
focused on the \emph{classical} R\'enyi entropy~\cite{jaconis-2013,stephan-2014}. Given 
a bipartition of the system into two complementary subregions $A$ and $B$, the classical 
R\'enyi entropy $S_n(A)$ (with $n\in\mathbb{N}$) is defined as 
%
\begin{equation}
S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
\Big)
\label{renyi-intro}
\end{equation}
%
Here ${\mathcal C}_A$ denotes the set of all the possible spin configurations in part 
$A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
definition), using another replica trick. This consists of $n$ independent and identical replicas (the 
booklet ``sheets'') of the model. These \emph{physical} replicas are different 
from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
The spins in part $A$ of different sheets are constrained to be equal. It is 
convenient to introduce the booklet aspect ratio $0\le\omega\le1$ as  
%
\begin{equation}
\label{a-ratio}
\omega\equiv \frac{N_A}{N}.
\end{equation}
%
Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by replacing 
the sum over the proababilities of each state in region $A$ with the trace over the reduced 
density matrix for region $A$. For $n=1$ 
Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
${\mathcal I}_n(A,B)$ as 
%
\begin{equation}
{\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
\end{equation}
%
For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
\propto\ell$, with $\ell$ the length of the boundary between $A$ and $B$. Remarkably, 
for different $\ell$, the ratio ${\mathcal I}_n/\ell$ has been shown to exhibit a crossing at a second 
order phase transition~\cite{jaconis-2013}, implying that it can be used as a diagnostic 
tool for critical behaviors. For conformally invariant critical models more universal 
information can be extracted from the area-law corrections of ${\mathcal I}_n$~\cite{stephan-2014}.

@@

We start discussing the thermodynamic phase diagram of the S-K model on the $n$-sheets 
booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
by the standard paramagnetic one at high temperatures by a phase transition. The critical 
temperature exhibits a non trivial dependence on $\omega$ that we are able to determine 
analytically. In the high-temperature region the permutation symmetry among the replicas, 
both the physical and the fictitious ones, is preserved. This allows us to provide an exact 
analytic expression for the free energy of the model and several derived quantities, such as 
the internal energy. We compare our results with Monte Carlo simulations, finding perfect 
agreement. Oppositely, in the low-temperature phase the replica symmetry is broken. For 
instance, we numerically observe that the replica-symmetric (RS) result for the internal 
energy is systematically lower than the Monte Carlo data, as in the standard S-K 
model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger upon 
lowering the temperature.

@@

Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This obeys a volume 
law for any $\beta$ and $\omega$, in contrast with local spin models, where an area law is 
observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, $[{\mathcal I}_2]/N$ 
exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures 
one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ is in good agreement with the Monte Carlo 
data for $\beta\lesssim 3$.

@@

Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
the classical R\'enyi entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
%
\begin{equation}
\label{renyi}
S_n(A)\equiv \frac{1}{1-n}\log\left(\frac{Z(A,n,\beta)}{Z^n(\beta)}\right).
\end{equation}
%
Here $Z(A,n,\beta)$ is the partition function of the model on the $n$-sheet booklet, 
whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures 
$\beta$. The booklet geometry is illustrated in Fig.~\ref{cartoon}, and consists of 
$n$ identical copies (``sheets'') of the system. Each sheet is divided into two 
parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). The spins in part $A$ of the different 
sheets are identified (cf. Fig.~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
are at inverse temperature $\beta$, the ones in $A$ are at the effective temperature $n\beta$. 
Notice that a similar geometric construction~\cite{guerra-2002} plays an important role in the 
mathematical proof of the Parisi ansatz. Moreover, the study of the partition function of 
critical models on the booklet has attracted considerable attention recently~\cite{fradkin-2006,
fradkin-2009,hsu-2009,stephan-2009,hsu-2010,oshikawa-2010,stephan-2010,zaletel-2011}.

Clearly, one has $S_n(A)\equiv1/(n-1)\log(F(A,n,\beta))-n\log(F(\beta))$, where $F(A,n,\beta)
\equiv\log(Z(A,n\beta))$ and $F(\beta)\equiv\log(Z(\beta))$ are related (apart from a factor 
$\beta$) to the free energy of the model on the booklet and on the plane, respectively.
The mutual information ${\mathcal I}_n(A,B,\beta)$ is defined~\cite{jaconis-2013,stephan-2014} 
as 
%
\begin{equation}
\label{MI}
{\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z^n(\beta)Z(n\beta)}
\Big),
\end{equation}
%
where $Z(B,n,\beta)$ is obtained from $Z(A,n,\beta)$ by replacing $A$ with $B$. 
Notice that the disorder-averaged mutual information $[{\mathcal I}_n]$ and the R\'enyi 
entropy $[S_n]$ are directly related to the so-called quenched-averaged free energy 
$[F(A,n,\beta)]$, which is the main quantity of interest in disordered systems~\cite{cardy-book}.

For clean (i.e., without disorder) \emph{local} spin models ${\mathcal I}_n$ 
obeys the boundary law 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=\alpha_n\ell+{\mathcal G}_n+\gamma_n,
\label{GMI}
\end{equation}
%
with $\ell$ the length of the boundary between $A$ and $B$, and 
$\alpha_n,\gamma_n$ two non-universal constants. Here ${\mathcal G}_n$ 
is the so-called geometric mutual information~\cite{stephan-2014}. 
Interestingly, for critical systems ${\mathcal G}_n$ depends only on the 
geometry of $A$ and $B$, and it is universal. For conformally invariant models 
${\mathcal G}_n$ can be calculated using standard methods of conformal field 
theory (CFT), and it allows to numerically extract universal information 
about the CFT, such as the central charge~\cite{stephan-2014}.

@@

The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
sherrington-1978} on the $n$-sheets booklet (cf. Fig.~\ref{cartoon}) is 
defined by the Hamiltonian
%
\begin{equation}
{\mathcal H}=-\sum\limits_{r=1}^n\left\{\sum\limits_{i<j}J_{ij}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\right\}.
\label{SK-ham}
\end{equation}
%
Here $S_i^{(r)}=\pm 1$ are classical Ising spins, $r\in[1,n]$ labels the 
different sheets (``pages'') of the booklet, $i\in[1,N]$ denotes the sites on 
each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
magnetic field. Here we choose $h=0$. The total number of spins in the booklet 
is $nN$. The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
$N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
In each ``sheet'' all the sites are divided into two groups $A\equiv\{1,\dots, N_A\}$ 
and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ sites, 
respectively. The spins living in part $A$ and different sheets are identified, i.e., 
$\forall i\in A$ one has  
%
\begin{equation}
S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
\label{book-constraint}
\end{equation}
%
Since in each sheet all spins interact with each other, there is no notion of distance 
between different spins. Thus, physical observables should depend on the booklet geometry 
only through the ratio $\omega$ (cf. Eq.~\eqref{a-ratio}).

In Eq.~\eqref{SK-ham} the couplings $J_{ij}\in\mathbb{R}$ are uncorrelated (from site to site) 
quenched random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
here $J_{ij}$ are drawn from the gaussian distribution   
%
\begin{equation}
P(J_{ij})=
\left(\frac{N}{2\pi}\right)^{1/2}
\exp\Big\{-\frac{N}{2J^2}
\Big(J_{ij}-\frac{J_0}{N}\Big)^2\Big\}.
\label{quenched-distr}
\end{equation}
%
The mean and the variance of $P(\{J_{ij}\})$ are given as $[J_{ij}]=J_0/N$ 
and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. The square brackets $[\cdot]$ denote 
the average over different realizations of $J_{ij}$.  Here we restrict ourselves to 
$J_0=0$ and $J=1$. The factors $N$ in Eq.~\eqref{quenched-distr} ensure a well-defined 
thermodynamic limit.

@@

The disorder-averaged free energy $[F(\omega,n,\beta)]$ (cf. 
Eq.~\eqref{free-energy}) of the model is obtained, using the standard replica 
trick~\cite{cardy-book}, as  
%
\begin{equation}
\label{replica-trick}
[F(\omega,n,\beta)]=\lim_{\alpha\to 0}\frac{[Z^\alpha(\omega,n,\beta)]-1}
{\alpha}. 
\end{equation}
%
Here $[Z^\alpha(\omega,n,\beta)]$ is the disorder-averaged partition 
function of $\alpha\in\mathbb{N}$ independent copies of the S-K model on the 
booklet. Precisely, $[Z^\alpha(\omega,n,\beta)]$ reads 
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]=\int{\mathcal D}\{J\}
\tr'\exp\sum\limits_{r,\gamma}
\Big\{\\
\beta\sum\limits_{i<j}J_{ij}S_i^{(r,\gamma)}S_j^{(r,\gamma)}
+\beta h\sum\limits_{i}S^{(r,\gamma)}_i\Big\},
\label{rep-Z}
\end{multline}
%
where the index $\gamma=1,2,\dots,\alpha$ labels the different fictitious 
replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
physical replicas, as in Eq.~\eqref{book-pf}. Again, physical and fictitious 
replicas do not interact with each other. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
thought of as the partition function of the S-K model on a ``replicated'' 
booklet.

>>>>

We investigate the \emph{classical} R\'enyi entropy $S_n$ and the associated mutual 
information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
paradigm model of mean-field spin glasses. 
Using classical Monte Carlo simulations and analytical tools we investigate the 
S-K model on the $n$-sheets booklet.
This is obtained by gluing together $n$ independent copies of the model, and it is the 
main ingredient to construct the R\'enyi entanglement-related quantities. We find a 
glassy phase at low temperature, whereas at high temperature the model exhibits 
paramagnetic behavior, consistent with the regular S-K model. The temperature of the 
paramagnetic-glassy transition depends 
non-trivially on the geometry of the booklet. At high-temperatures we provide the exact 
solution of the model by exploiting the replica symmetry. This is the permutation symmetry 
among the fictitious replicas that are used to perform disorder averages (via the replica 
trick). In the glassy phase the replica symmetry has to be broken. Using a generalization 
of the Parisi solution, we provide analytical results for $S_n$ and ${\mathcal I}_n$, 
and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
volume law in the whole phase diagram. We characterize the behavior of the 
corresponding densities $S_n/N,{\mathcal I}_n/N$, in the thermodynamic limit. 
Interestingly, at the critical point the mutual information does not exhibit any 
crossing for different system sizes, in contrast with local spin models.

@@

Besides being ubiquitous in nature, disorder leads to several intriguing 
physical phenomena. 
Arguably, \emph{spin glasses} represent one of the most prototypical examples
of interesting behavior induced by disorder.
While at any finite temperature disorder can prevent the 
usual magnetic ordering, at low-enough temperatures these systems display a 
new type of ``order''. In the past decades an intense theoretical 
effort has been devoted to characterizing this spin glass order, the nature of 
the paramagnetic-glassy transition, and that of the associated order 
parameter~\cite{binder-1986,parisi-book,young-1998,nishimori-book,castellani-2005}.

All these issues can be thoroughly addressed in the Sherrington-Kirkpatrick 
(S-K) model~\cite{sherrington-1978,sherrington-1978-prl}, which is exactly 
solvable. The S-K model is a \emph{classical} Ising model on the fully-connected 
graph of $N$ sites, with quenched random interactions. Its hamiltonian reads  
%
\begin{equation}
{\mathcal H}=-\sum\limits_{1\le i<j\le N}J_{ij}S_i S_j-
h\sum\limits_{1\le i\le N}S_i.
\label{SK-intro}
\end{equation}
%
Here $S_i=\pm 1$ are classical Ising spins, $h$ is an external magnetic field, and 
$J_{ij}$ are uncorrelated (from site to site) random variables. The S-K model hosts 
a low-temperature glassy phase, which is separated from a high-temperature paramagnetic 
one by a second order phase transition. Despite its mean-field nature, the solution 
of the S-K model has been a mathematical challenge. Although it was proposed as an 
ansatz by Parisi~\cite{parisi-1980} more than thirty years ago, its rigorous proof 
was obtained only recently~\cite{talagrand-2006}. Moreover, the solution exhibits several 
intricate features, such as lack of self-averaging~\cite{pastur-1991}, ultrametricity~\cite{
mezard-1984,rammal-1986}, and replica symmetry breaking~\cite{parisi-book,castellani-2005}. 
The last refers to the breaking of the permutation symmetry among the fictitious replicas 
of the model, which are introduced to perform disorder averages (via the so-called 
\emph{replica trick}~\cite{cardy-book}. Finally, although the 
applicability of the S-K model to describe realistic spin glasses is still highly 
debated~\cite{yucesoy-2012,billoire-2012,yucesoy-2013}, there are recent proposals on 
how to realize it in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser 
systems~\cite{ghofraniha-2015}.

In the last decade entanglement-related quantities emerged as valuable tools to 
understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
cc-rev}, both classical and quantum. For instance, at a conformally invariant critical 
point entanglement measures contain universal information about the underlying 
conformal field theory (CFT), such as the central charge~\cite{holzhey-1994,vidal-2003,
calabrese-2004,calabrese-2012}. For classical spin models a lot of attention has been 
focused on the \emph{classical} R\'enyi entropy~\cite{jaconis-2013,stephan-2014}. Given 
a bipartition of the system into two complementary subregions $A$ and $B$, the classical 
R\'enyi entropy $S_n(A)$ (with $n\in\mathbb{N}$) is defined as 
%
\begin{equation}
S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
\Big)
\label{renyi-intro}
\end{equation}
%
Here ${\mathcal C}_A$ denotes the set of all the possible spin configurations in part 
$A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
definition). This consists of $n$ independent and identical copies (the 
booklet ``sheets'') of the model. These \emph{physical} copies are different 
from the \emph{fictitious} replicas used to perform the disorder average. Each sheet is 
divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
The spins in part $A$ of different sheets are constrained to be equal. It is 
convenient to introduce the booklet aspect ratio $0\le\omega\le1$ as  
%
\begin{equation}
\label{a-ratio}
\omega\equiv \frac{N_A}{N}.
\end{equation}
%
Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by replacing 
the sum over the proababilities of each state in region $A$ with the trace over the reduced 
density matrix for region $A$. For $n=1$ 
Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
${\mathcal I}_n(A,B)$ as 
%
\begin{equation}
\label{MI}
{\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
\end{equation}
%
For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
\propto\ell$, with $\ell$ the length of the boundary between $A$ and $B$. Remarkably, 
for different $\ell$, the ratio ${\mathcal I}_n/\ell$ has been shown to exhibit a crossing at a second 
order phase transition~\cite{jaconis-2013}, implying that it can be used as a diagnostic 
tool for critical behaviors. For conformally invariant critical models more universal 
information can be extracted from the area-law corrections of ${\mathcal I}_n$~\cite{stephan-2014}.

@@

We start discussing the thermodynamic phase diagram of the S-K model on the $n$-sheets 
booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
by the standard paramagnetic one at high temperatures by a phase transition. The critical 
temperature exhibits a non trivial dependence on $\omega$ that we are able to determine 
analytically. In the high-temperature region the permutation symmetry among both the replicas  
and the physical sheets  is preserved. This allows us to provide an exact 
analytic expression for the free energy of the model and several derived quantities, such as 
the internal energy. We compare our results with Monte Carlo simulations, finding perfect 
agreement. Oppositely, in the low-temperature phase the replica symmetry is broken. For 
instance, we numerically observe that the replica-symmetric (RS) result for the internal 
energy is systematically lower than the Monte Carlo data, as in the standard S-K 
model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger upon 
lowering the temperature.

@@

Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This obeys a volume 
law for any $\beta$ and $\omega$, in contrast with local spin models, where an area law is 
observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, $[{\mathcal I}_2]/N$ 
exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$. Deviations from the RS result, 
if present, are $\lesssim 10^{-3}$. On the other hand, at low temperatures 
one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ is in good agreement with the Monte Carlo 
data for $\beta\lesssim 3$.

@@

Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
the classical R\'enyi entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
%
\begin{equation}
\label{renyi}
S_n(A)\equiv \frac{1}{1-n}\log\left(\frac{Z(A,n,\beta)}{Z^n(\beta)}\right).
\end{equation}
%
Here $Z(A,n,\beta)$ is the partition function of the model on the $n$-sheet booklet, 
whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures 
$\beta$. The booklet geometry is illustrated in Fig.~\ref{cartoon}, and consists of 
$n$ identical copies (``sheets'') of the system. Each sheet is divided into two 
parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). The spins in part $A$ of the different 
sheets are identified (cf. Fig.~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
are at inverse temperature $\beta$, the ones in $A$ are at the effective temperature $n\beta$. 
Notice that a similar geometric construction~\cite{guerra-2002} plays an important role in the 
mathematical proof of the Parisi ansatz. Moreover, the study of the partition function of 
critical models on the booklet has attracted considerable attention recently~\cite{fradkin-2006,
fradkin-2009,hsu-2009,stephan-2009,hsu-2010,oshikawa-2010,stephan-2010,zaletel-2011}.
Clearly, one has $S_n(A)\equiv1/(n-1)(\log(F(A,n,\beta))-n\log(F(\beta)))$, where $F(A,n,\beta)
\equiv\log(Z(A,n\beta))$ and $F(\beta)\equiv\log(Z(\beta))$ are related (apart from a factor 
$-1/\beta$) to the free energy of the model on the booklet and on the plane, respectively.

The mutual information ${\mathcal I}_n(A,B,\beta)$ is obtained in terms of the booklet 
partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. Notice that the disorder-averaged 
mutual information $[{\mathcal I}_n]$ and the R\'enyi entropy $[S_n]$ are directly related to 
the so-called quenched-averaged free energy $[F(A,n,\beta)]$, which is the main quantity of 
interest in disordered systems~\cite{cardy-book}. 
For clean (i.e., without disorder) \emph{local} spin models ${\mathcal I}_n$ 
obeys the boundary law 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=\alpha_n\ell+{\mathcal G}_n+\gamma_n,
\label{GMI}
\end{equation}
%
with $\ell$ the length of the boundary between $A$ and $B$, and 
$\alpha_n,\gamma_n$ two non-universal constants. Here ${\mathcal G}_n$ 
is the so-called geometric mutual information~\cite{stephan-2014}. 
Interestingly, for critical systems ${\mathcal G}_n$ depends only on the 
geometry of $A$ and $B$, and it is universal. For conformally invariant models 
${\mathcal G}_n$ can be calculated using standard methods of conformal field 
theory (CFT), and it allows to numerically extract universal information 
about the CFT, such as the central charge~\cite{stephan-2014}.

@@

The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
sherrington-1978} on the $n$-sheets booklet (cf. Fig.~\ref{cartoon}) is 
defined by the Hamiltonian
%
\begin{equation}
{\mathcal H}=-\sum\limits_{r=1}^n\left\{\sum\limits_{i<j}J_{ij}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\right\}.
\label{SK-ham}
\end{equation}
%
Here $S_i^{(r)}=\pm 1$ are classical Ising spins, $r\in[1,n]$ labels the 
different sheets (``pages'') of the booklet, $i\in[1,N]$ denotes the sites on 
each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
magnetic field. The total number of spins in the booklet is $nN$. 
The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
$N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
In each ``sheet'' all the sites are divided into two groups $A\equiv\{1,\dots, N_A\}$ 
and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ sites, 
respectively. The spins living in part $A$ and different sheets are identified, i.e., 
$\forall i\in A$ one has  
%
\begin{equation}
S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
\label{book-constraint}
\end{equation}
%
Since in each sheet all spins interact with each other, there is no notion of distance 
between different spins. Thus, physical observables should depend on the booklet geometry 
only through the ratio $\omega$ (cf. Eq.~\eqref{a-ratio}).

In Eq.~\eqref{SK-ham} the couplings $J_{ij}\in\mathbb{R}$ are uncorrelated (from site to site) 
quenched random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
here $J_{ij}$ are drawn from the gaussian distribution   
%
\begin{equation}
P(J_{ij})=
\left(\frac{N}{2\pi}\right)^{1/2}
\exp\Big\{-\frac{N}{2J^2}
\Big(J_{ij}-\frac{J_0}{N}\Big)^2\Big\}.
\label{quenched-distr}
\end{equation}
%
The mean and the variance of $P(\{J_{ij}\})$ are given as $[J_{ij}]=J_0/N$ 
and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. Here we set $J=1$. The square brackets $[\cdot]$ denote 
the average over different realizations of $J_{ij}$. Here we restrict ourselves to 
$J_0=0$ and $J=1$. The factors $N$ in Eq.~\eqref{quenched-distr} ensure a well-defined 
thermodynamic limit.

@@

The disorder-averaged free energy $[F(\omega,n,\beta)]$ (cf. 
Eq.~\eqref{free-energy}) of the model is obtained, using the standard replica 
trick~\cite{cardy-book}, as  
%
\begin{equation}
\label{replica-trick}
[F(\omega,n,\beta)]=\lim_{\alpha\to 0}\frac{[Z^\alpha(\omega,n,\beta)]-1}
{\alpha}. 
\end{equation}
%
Here $[Z^\alpha(\omega,n,\beta)]$ is the disorder-averaged partition 
function of $\alpha\in\mathbb{N}$ independent copies of the S-K model on the 
booklet. Precisely, $[Z^\alpha(\omega,n,\beta)]$ reads 
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]=\int{\mathcal D}\{J\}
\tr'\exp\sum\limits_{r,\gamma}
\Big\{\\
\beta\sum\limits_{i<j}J_{ij}S_i^{(r,\gamma)}S_j^{(r,\gamma)}
+\beta h\sum\limits_{i}S^{(r,\gamma)}_i\Big\},
\label{rep-Z}
\end{multline}
%
where the index $\gamma=1,2,\dots,\alpha$ labels the different fictitious 
replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
physical copies, i.e., the booklet sheets, as in Eq.~\eqref{book-pf}. Again, 
spins on different sheets or different replicas do not interact with each other. 
Notice that $Z^{\alpha}(\omega,n,\beta)$ can be thought of as the partition 
function of the S-K model on a ``replicated'' booklet.
